Predictive Regressions with Persistent Regressors

### 2019-09-11 paper.tex
clean up

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.5in]{geometry}
\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

Implementing it, first $\hat{\beta}$ and its standard error $\operatorname{SE}(\widehat{\beta})$ are obtained by OLS estimation of equation ($\ref{eqn:1}$). $x_{t}$ is written in its augmented Dickey-Fuller form
\begin{equation}
\Delta x_{t}=\tau+\theta x_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta x_{t-i}+e_{t},
\end{equation}
where $\psi_{i}=-\sum_{j=i}^{p-1} a_{j}$, $a(L)=L^{-1}[1-(1-\rho L) b(L)]$, and $\theta=(\rho-1) b(1)$. Estimation of $\widehat{\psi}_{i}(i=1, \ldots, p-1)$ is done via OLS where $p$ is either explicitly specified or estimated via the Bayesian information criterion [BIC].
With $\widehat{u}_{t}$ and $\widehat{e}_{t}$ being the residuals of regression (1) and (2), respectively,
\begin{align} \widehat{\sigma}_{u}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t}^{2} \\ \widehat{\sigma}_{e}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{e}_{t}^{2} \\ \widehat{\sigma}_{u e} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t} \widehat{e}_{t} \\ \widehat{\delta} &=\frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{u} \widehat{\sigma}_{e}} \\ \widehat{\omega}^{2}&=\widehat{\sigma}_{e}^{2} /\left(1-\sum_{i=1}^{p-1} \widehat{\psi}_{i}\right)^{2}
\end{align}
are then computed. OLS estimation of equation ($\ref{eqn:22}$) yields $\widehat{\rho}$ and its standard error $\mathrm{SE}(\widehat{\rho})$. The residual $\widehat{v}_{t}$ is used to compute 
\begin{equation}
\widehat{\sigma}_{v}^{2}=(T-2)^{-1} \sum_{t=1}^{T} \widehat{v}_{t}^{2}.
\end{equation} 
Now, to compute the DF-GLS statistic, $\left(x_{0}, x_{1}-\rho_{G L S} x_{0}, \ldots, x_{T}-\rho_{G L S} x_{T-1}\right)^{\prime}$ is regressed onto 
$\left(1,1-\rho_{G L S}, \ldots, 1-\rho_{G L S}\right)^{\prime}$ with $\rho_{G L S}=1-7 / T$. The coefficient $\mu_{G L S}$ is used to compute $\overline{x}_{t}=x_{t}-\mu_{G L S}$ which, in turn, is needed for the regression 
\begin{equation}
\Delta \overline{x}_{t}=\theta \overline{x}_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta \overline{x}_{t-i}+e_{t},
\end{equation} which is estimated with no intercept. Finally, the t-statistic for $\theta$ is computed. This is the DF-GLS statistic. To confirm that no error is conducted in this estimation procedure, the DF-GLS statistic thus obtained is compared to the implementation in the urca$\footnote{}$ package.

$[\underline{\rho}, \overline{\rho}]=[1+\underline{c} / T, 1+\overline{c} / T]$ is obtained by first finding $[\underline{c}, \overline{c}]$ via tables 2–11 of Campbell and Yogo (2005) where the closest values to the estimated DF-GLS statistic and $\hat{\delta}$ are used. Let a temporary variable $r^{\star}$ be defined by
\begin{equation}
r_{t}^{*}=r_{t}-\widehat{\sigma}_{u e} \widehat{\sigma}_{e}^{-2}\left(x_{t}-\rho x_{t-1}\right).
\end{equation}
Now the regression
\begin{equation}
r_{t}^{*}=\alpha+\beta x_{t-1}+u_{t}
\end{equation} 
is run for each $\rho=\{\underline{\rho}, \overline{\rho}\}$ to get $\widehat{\beta}(\rho)$. $[\underline{\beta}(\rho), \overline{\beta}(\rho)]$ is then obtained by computing

@@

\section{Monte Carlo simulation}
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by Phillips (2014), the Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrate as $\rho$ diverges from unity. Again 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. 

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
Glosten, Jagannathan and Runkle (1993) [GJR] observe that in financial markets negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$ negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability.

@@

\section{Empirical Results}
\label{Empirical Results}
Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of Campbell and Yogo (2006). The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistic for $p>1$ is higher than reported by Campbell and Yogo (2006).  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. 
\begin{table}[ht]
\small
\setlength\tabcolsep{5pt}
\centering
\caption{Replicated estimates of model parameters from Campbell and Yogo (2006)}
\label{tab:cy_sp}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
  SP\_A & lep & 123 & -0.96 & [0.786,0.931] & -2.888 & 1 & 2.76 & 0 & 0.127 & [0.043,0.225] \\ 
  SP\_A & ldp & 123 & -0.85 & [0.940,1.006] & -1.247 & 3 & 1.95 & 0 & 0.083 & [-0.024,0.136] \\ 
  CRSP\_A & lep & 77 & -0.96 & [0.778,0.960] & -2.229 & 1 & 2.77 & 0 & 0.162 & [0.040,0.273] \\ 
  CRSP\_A & ldp & 77 & -0.72 & [0.926,1.010] & -1.033 & 1 & 2.53 & 0 & 0.158 & [0.013,0.186] \\ 
  CRSP\_Q & lep & 305 & -0.99 & [0.944,0.992] & -2.191 & 1 & 2.91 & 0 & 0.047 & [0.011,0.066] \\ 
  CRSP\_Q & ldp & 305 & -0.94 & [0.962,0.999] & -1.696 & 1 & 2.06 & 0 & 0.034 & [-0.009,0.044] \\ 
  CRSP\_M & lep & 913 & -0.99 & [0.985,1.000] & -1.859 & 1 & 2.66 & 0 & 0.013 & [0.001,0.018] \\ 
  CRSP\_M & ldp & 913 & -0.95 & [0.990,1.001] & -1.433 & 1 & 1.70 & 0 & 0.008 & [-0.005,0.010] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website at https://drive.google.com/file/d/0BzR-ojpYuaFMcnZteHFyWUVIUFU/view. The regressors are the 10-year moving average earnings to current price ratio [lep] and the dividend to price ratio [ldp] in logs. Observations are recorded on a monthly [CRSP M], quarterly [CRSP Q], and annual basis [CRSP A] for CRSP (1926– 2002). For S\&P (1880– 2002) data is only available on an annual basis [SP A]. Stock returns are the SP 500 value weighted index log-returns from 1880 to 2003 minus the risk free rate and the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate. $p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}

The null hypothesis of no predictability can be rejected at the 10\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively, using data from Campbell and Yogo (2006). Based on the extended dataset from Amid Goyal, only lep on a quarterly frequency can be inferred to be predictive of excess log-returns. This discrepancy may arise from two causes. First due to the lack of availability of the 1-month T-bill rate, all risk free-rate computations are based on the 3-month T-bill in the extended dataset. This introduces minor differences in datasets since Campbell and Yogo (2006) use the 1-month T-bill as a risk-free proxy for their monthly regressions. Second, as will be seen in Table~\vref{tab:oos} predictability seems to have been weakening in recent years. Hence, a time-extended sample will show less evidence of it.  
\begin{table}[ht]
\small
\setlength\tabcolsep{5pt}
\centering
\caption{Replicated estimates of model parameters from Campbell and Yogo (2006) with an extended dataset}
\label{tab:extended}
\begin{threeparttable}
\begin{tabular}{llrrlrrrrrl}
%\begin{tabular}{ccccccccccc}
  \hline
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  \hline
    CRSP\_A  & lep & 92 & -0.97 & [0.827,0.979] & -2.092 & 1 & 2.12 & 0 & 0.114 & [-0.01,0.180] \\ 
    CRSP\_A  & ldp & 92 & -0.86 & [0.875,0.986] & -1.731 & 1 & 0.97 & 0 & 0.042 & [-0.069,0.107] \\ 
    %CRSP\_A  & tbl & 66 & 0.08 & [0.853,0.908] & -1.899 & 1 & -0.41 & 1 & -0.279 & [-0.125,0.075] \\ 
    %CRSP\_A  & tms & 66 & -0.06 & [0.454,0.575] & -3.942 & 1 & 0.96 & 1 & 1.297 & [-0.071,0.275] \\ 
   CRSP\_Q & lep & 365 & -0.98 & [0.973,1.002] & -1.515 & 1 & 3.16 & 0 & 0.048 & [0.001,0.039] \\ 
  CRSP\_Q & ldp & 365 & -0.95 & [0.976,1.002] & -1.386 & 1 & 1.82 & 0 & 0.023 & [-0.012,0.026] \\ 
  %CRSP\_Q & tbl & 261 & -0.09 & [0.956,0.975] & -1.985 & 1 & -0.64 & 1 & -0.099 & [-0.045,0.019] \\ 
  %CRSP\_Q& tms & 261 & 0.06 & [0.835,0.864] & -4.392 & 1 & 1.44 & 1 & 0.489 & [-0.005,0.104] \\ 
  CRSP\_M & lep & 1104 & -0.99 & [0.993,1.002] & -1.343 & 1 & 2.40 & 0 & 0.010 & [-0.002,0.009] \\ 
  CRSP\_M & ldp & 1104 & -0.98 & [0.993,1.002] & -1.221 & 1 & 1.20 & 0 & 0.004 & [-0.005,0.006] \\ 
  %CRSP\_M & tbl & 792 & -0.13 & [0.992,0.997] & -1.428 & 1 & -0.91 & 1 & -0.043 & [-0.013,0.003] \\ 
  %CRSP\_M & tms & 792 & 0.04 & [0.958,0.967] & -3.831 & 1 & 1.49 & 1 & 0.156 & [-0.001,0.032] \\ 
\hline
\end{tabular}
 \begin{tablenotes}
 \small
\item Data is taken from Amit Goyal’s Website. Stock returns are the SP 500 index log-returns from 1926 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (1926 to 2017). ldp is the log dividend/price ratio (1926 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{mathrsfs}  
\usepackage{float}
\usepackage{varioref}
\usepackage[margin=1.2in]{geometry}
\usepackage[flushleft]{threeparttable}
\title{Predictive Regressions with Persistent Regressors}
\author{Jan Philipp Wöltjen  \\
	Seminar in Statistics CAU Kiel  \\
	}

@@

Implementing the feasible Q-test, first $\hat{\beta}$ and its standard error $\operatorname{SE}(\widehat{\beta})$ are obtained by OLS estimation of equation ($\ref{eqn:1}$). $x_{t}$ is written in its augmented Dickey-Fuller form
\begin{equation}
\Delta x_{t}=\tau+\theta x_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta x_{t-i}+e_{t},
\end{equation}
where $\psi_{i}=-\sum_{j=i}^{p-1} a_{j}$, $a(L)=L^{-1}[1-(1-\rho L) b(L)]$, and $\theta=(\rho-1) b(1)$. Estimation of $\widehat{\psi}_{i}(i=1, \ldots, p-1)$ is done via OLS where $p$ is either explicitly specified or estimated via the Bayesian information criterion [BIC].
With $\widehat{u}_{t}$ and $\widehat{e}_{t}$ being the residuals of regression (1) and (2), respectively,
\begin{align} \widehat{\sigma}_{u}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t}^{2} \\ \widehat{\sigma}_{e}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{e}_{t}^{2} \\ \widehat{\sigma}_{u e} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t} \widehat{e}_{t} \\ \widehat{\delta} &=\frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{u} \widehat{\sigma}_{e}} \\ \widehat{\omega}^{2}&=\widehat{\sigma}_{e}^{2} /\left(1-\sum_{i=1}^{p-1} \widehat{\psi}_{i}\right)^{2}
\end{align}
are then computed. OLS estimation of equation ($\ref{eqn:22}$) yields $\widehat{\rho}$ and its standard error $\mathrm{SE}(\widehat{\rho})$. The residual $\widehat{v}_{t}$ is used to compute 
\begin{equation}
\widehat{\sigma}_{v}^{2}=(T-2)^{-1} \sum_{t=1}^{T} \widehat{v}_{t}^{2}.
\end{equation} 
Now, to compute the DF-GLS statistic, $\left(x_{0}, x_{1}-\rho_{G L S} x_{0}, \ldots, x_{T}-\rho_{G L S} x_{T-1}\right)^{\prime}$ is regressed onto 
$\left(1,1-\rho_{G L S}, \ldots, 1-\rho_{G L S}\right)^{\prime}$ with $\rho_{G L S}=1-7 / T$. The coefficient $\mu_{G L S}$ is used to compute $\overline{x}_{t}=x_{t}-\mu_{G L S}$ which, in turn, is needed for the regression 
\begin{equation}
\Delta \overline{x}_{t}=\theta \overline{x}_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta \overline{x}_{t-i}+e_{t},
\end{equation} which is estimated with no intercept. Finally, the t-statistic for $\theta$ is computed. This is the DF-GLS statistic. To confirm that no error is conducted in this estimation procedure, the DF-GLS statistic thus obtained is compared to the implementation in the urca package of Pfaff (2008).

The confidence interval $[\underline{\rho}, \overline{\rho}]=[1+\underline{c} / T, 1+\overline{c} / T]$ is obtained by first finding $[\underline{c}, \overline{c}]$ via tables 2–11 of Campbell and Yogo (2005), where the closest values to the estimated DF-GLS statistic and $\hat{\delta}$ are used. Let a temporary variable $r^{\star}$ be defined by
\begin{equation}
r_{t}^{*}=r_{t}-\widehat{\sigma}_{u e} \widehat{\sigma}_{e}^{-2}\left(x_{t}-\rho x_{t-1}\right).
\end{equation}
Now the regression
\begin{equation}
r_{t}^{*}=\alpha+\beta x_{t-1}+u_{t}
\end{equation} 
is run for each $\rho=\{\underline{\rho}, \overline{\rho}\}$ to get $\widehat{\beta}(\rho)$. $[\underline{\beta}(\rho), \overline{\beta}(\rho)]$ is then obtained by computing

@@

\section{Monte Carlo simulation}
This section accommodates, next to the out-of-sample results in section $\ref{Empirical Results}$, one of the main contributions of this study. First, Monte Carlo evidence of Campbell and Yogo (2006) is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of Campbell and Yogo (2006) with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by Phillips (2014), the Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrate as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of Campbell and Yogo (2005). Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
Glosten, Jagannathan and Runkle (1993) [GJR] observe that in financial markets negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the square of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$ negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%.

@@

\section{Empirical Results}
\label{Empirical Results}
Table~\vref{tab:cy_sp} replicates the key results of Tables 4 and 5 of Campbell and Yogo (2006). The Bonferroni Q-test is implemented as described in section $\ref{implementation}$. Apart from rounding errors, the results are nearly the same except for the following discrepancies. First, the DF-GLS statistic for $p>1$ is higher than reported by Campbell and Yogo (2006).  As previously mentioned, the DF-GLS implementation of section $\ref{implementation}$ was verified with a different open-source implementation. Second, based on the BIC, a lower $p$ of 1 was selected for monthly ldp. Investigations showed that the difference in BIC when $p=1$ compared with $p=2$ is very small. Thus the different selection is likely due to rounding errors. 
\begin{table}[hb]
\setlength\tabcolsep{5.3pt}
\caption{Replicated estimates of model parameters from Campbell and Yogo (2006)}
\label{tab:cy_sp}
\begin{tabular}{llrrlrrrrrl}
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
  SP\_A & lep & 123 & -0.96 & [0.786,0.931] & -2.888 & 1 & 2.76 & 0 & 0.127 & [0.043,0.225] \\ 
  SP\_A & ldp & 123 & -0.85 & [0.940,1.006] & -1.247 & 3 & 1.95 & 0 & 0.083 & [-0.024,0.136] \\ 
  CRSP\_A & lep & 77 & -0.96 & [0.778,0.960] & -2.229 & 1 & 2.77 & 0 & 0.162 & [0.040,0.273] \\ 
  CRSP\_A & ldp & 77 & -0.72 & [0.926,1.010] & -1.033 & 1 & 2.53 & 0 & 0.158 & [0.013,0.186] \\ 
  CRSP\_Q & lep & 305 & -0.99 & [0.944,0.992] & -2.191 & 1 & 2.91 & 0 & 0.047 & [0.011,0.066] \\ 
  CRSP\_Q & ldp & 305 & -0.94 & [0.962,0.999] & -1.696 & 1 & 2.06 & 0 & 0.034 & [-0.009,0.044] \\ 
  CRSP\_M & lep & 913 & -0.99 & [0.985,1.000] & -1.859 & 1 & 2.66 & 0 & 0.013 & [0.001,0.018] \\ 
  CRSP\_M & ldp & 913 & -0.95 & [0.990,1.001] & -1.433 & 1 & 1.70 & 0 & 0.008 & [-0.005,0.010] \\ 
\item Data is taken from Motohiro Yogo's website at https://drive.google.com/file/d/0BzR-ojpYuaFMcnZteHFyWUVIUFU/view. The regressors are the 10-year moving average earnings to current price ratio [lep] and the dividend to price ratio [ldp] in logs. Observations are recorded on a monthly [CRSP M], quarterly [CRSP Q], and annual basis [CRSP A] for CRSP (1926– 2002). For S\&P (1880– 2002) data is only available on an annual basis [SP A]. Stock returns are the SP 500 value weighted index log-returns from 1880 to 2003 minus the risk free rate and the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate. $p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor. The null hypothesis of no predictability can be rejected at the 10\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively, using data from Campbell and Yogo (2006). Based on the extended dataset from Amid Goyal, only lep on a quarterly frequency can be inferred to be predictive of excess log-returns. This discrepancy may arise from two causes. First, returns in the extended dataset are of the S\&P500 instead of the CRSP value-weighted index. Also, due to the lack of availability of the 1-month T-bill rate, all risk free-rate computations are based on the 3-month T-bill in the extended dataset. This introduces minor differences in datasets since Campbell and Yogo (2006) use the 1-month T-bill as a risk-free proxy for their monthly regressions. Second, as will be seen in Table~\vref{tab:oos}, predictability seems to have been weakening in recent years. Hence, a time-extended sample will show less evidence of it.  
\begin{table}[h]
\setlength\tabcolsep{5.3pt}
\caption{Replicated estimates of model parameters from Campbell and Yogo (2006) with an extended dataset}
\label{tab:extended}
\begin{tabular}{llrrlrrrrrl}
%\begin{tabular}{ccccccccccc}
dataset & $x$ & obs & $\hat{\delta}$ & $CI_{\rho}$ & DF-GLS & $p$ &t-stat & pt & $\hat{\beta}$ & $CI_{\beta}$ \\ 
    CRSP\_A  & lep & 92 & -0.97 & [0.827,0.979] & -2.092 & 1 & 2.12 & 0 & 0.114 & [-0.01,0.180] \\ 
    CRSP\_A  & ldp & 92 & -0.86 & [0.875,0.986] & -1.731 & 1 & 0.97 & 0 & 0.042 & [-0.069,0.107] \\ 
    %CRSP\_A  & tbl & 66 & 0.08 & [0.853,0.908] & -1.899 & 1 & -0.41 & 1 & -0.279 & [-0.125,0.075] \\ 
    %CRSP\_A  & tms & 66 & -0.06 & [0.454,0.575] & -3.942 & 1 & 0.96 & 1 & 1.297 & [-0.071,0.275] \\ 
   CRSP\_Q & lep & 365 & -0.98 & [0.973,1.002] & -1.515 & 1 & 3.16 & 0 & 0.048 & [0.001,0.039] \\ 
  CRSP\_Q & ldp & 365 & -0.95 & [0.976,1.002] & -1.386 & 1 & 1.82 & 0 & 0.023 & [-0.012,0.026] \\ 
  %CRSP\_Q & tbl & 261 & -0.09 & [0.956,0.975] & -1.985 & 1 & -0.64 & 1 & -0.099 & [-0.045,0.019] \\ 
  %CRSP\_Q& tms & 261 & 0.06 & [0.835,0.864] & -4.392 & 1 & 1.44 & 1 & 0.489 & [-0.005,0.104] \\ 
  CRSP\_M & lep & 1104 & -0.99 & [0.993,1.002] & -1.343 & 1 & 2.40 & 0 & 0.010 & [-0.002,0.009] \\ 
  CRSP\_M & ldp & 1104 & -0.98 & [0.993,1.002] & -1.221 & 1 & 1.20 & 0 & 0.004 & [-0.005,0.006] \\ 
  %CRSP\_M & tbl & 792 & -0.13 & [0.992,0.997] & -1.428 & 1 & -0.91 & 1 & -0.043 & [-0.013,0.003] \\ 
  %CRSP\_M & tms & 792 & 0.04 & [0.958,0.967] & -3.831 & 1 & 1.49 & 1 & 0.156 & [-0.001,0.032] \\ 
\item Data is taken from Amit Goyal’s Website. Stock returns are the SP 500 index log-returns from 1926 to 2017 from the Center for Research in Security Press (CRSP) minus the rolled over 3-month T-bill rate. lep is the log 10 year moving average earnings/price ratio (1926 to 2017). ldp is the log dividend/price ratio (1926 to 2017).
% tbl is the 3-month T-bill rate (1952 to 2017). tms is the term-spread between long-term government bonds and tbl (1952 to 2017). 
$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
